% Copyright 2017 (c) Michael Thomas (malinka) <malinka@entropy-development.com>
% Distributed under the terms of the Creative Commons Attribution Share-Alike v4.0
% notes.tex - plan for system documentation

\documentclass{article}

\usepackage{ulem}
\normalem

\begin{document}

\section{To Do}
\begin{itemize}
	\item Allow for translations
	\item \sout{Add keywords to glossary (tag keywords?)}
\end{itemize}

\section{Introduction}
A basic introduction, list of goals etc. How this document(s) are organized and why


\section{Characters}

\subsection{Statistics}
What is a Stat? Why do stats matter? How Hecate handles stats

\subsection{Skills}
What is a skill? Why do skills matter? What is different about a Skill versus a Stat?

\subsection{Traits}
What is a Trait? Why do we need traits?

\subsection{Templates}
What is a Template? Why do templates help us?


\section{Checks}
Is this a more cinematic campaign? or a more action oriented one? how does this effect checks?

\subsection{Modifiers}
What is a Modifier and why does it matter?

\subsection{Events}
What is an Event and why does it matter?


\section{Combat}
Is this a more cinematic campaign? or a more action oriented one? how does this effect combat?

\subsection{Turns}
Who goes first? Who goes Next? What can I do in one turn?

\subsection{Resources}
What is a resource, why does it matter, why isn't this in the Characters chapter?


\section{Campaigns}
Goals? Style?

\subsection{Setting}
Where are we? time? technology?

\subsection{Stats/Skills}
What skills are needed? what skills are available?

\subsection{Traits/Events}
How can players customize their characters to make them unique? What will impact the players and how?

\subsection{Combat/Resources}
Goals? Style? What information is needed to know how combat plays out for the characters?


\end{document}
